### 2023-04-25 paper.Rmd
changed directories of simulation results in paper file

```{r getresultsSim1}
files <- list.files("./Simulation_Study/Weight_Simulation", pattern = ".Rdata")
results <- list()
for (file in files) {
  results <- c(results, get(load(paste0("Simulation_Study/Weight_Simulation/", file))))
}

@@

## Analyze data for K = 2 and K = 3 and K = 4
simulation_results <- list()
for (K in 2:4) {
  filename <- paste0("./Simulation_Study/results-K", K, "-objectives-raw.csv")
  df <- read.csv(filename, sep = ";", stringsAsFactors = FALSE)
  df$K <- K
  simulation_results[[paste0("K-", K)]] <- df
}

>>>>

```{r getresultsSim1}
dir <- "./Simulation_1/"
files <- list.files(dir, pattern = ".Rdata")
results <- list()
for (file in files) {
  results <- c(results, get(load(paste0(dir, file))))
}

@@

## Analyze data for K = 2 and K = 3 and K = 4
simulation_results <- list()
for (K in 2:4) {
  filename <- paste0("./Simulation_2/results-K", K, "-objectives-raw.csv")
  df <- read.csv(filename, sep = ";", stringsAsFactors = FALSE)
  df$K <- K
  simulation_results[[paste0("K-", K)]] <- df
}
